% !Mode:: "TeX:UTF-8"
% !TEX program  = xelatex
\begin{英文摘要}{Dense Prediction, Neural Networks, Feature Aligned, Android}
  Dense prediction is an important problem in the field of computer vision, which has important value for the segmentation and understanding of images in the fields of automatic driving, medical image recognition, etc.; it includes semantic segmentation, instance segmentation, panoptic segmentation, and other sub-tasks. In recent years, breakthroughs have been made in this problem by using neural networks. However, in the process of upsampling the upper convolutional layer using interpolation, there is a problem that the features obtained by the upsampling are not aligned with the features of the bottom-up convolutional layer. For this problem, this paper reproduces the feature alignment module and feature selection module in the FaPN(Feature-aligned Pyramid Network) to selects and aligns the key features of the upper convolutional layer through the contextual information before and after upsampling. Validation of the COCO2017 dataset confirms the module's performance for small objects and object boundary prediction. Modularized it to develop a simple Android app. The server side provides services by loading pre-trained models, and the client provides an easy-to-use UI interface and related functions required by various types of users. App has the function of quickly segmenting images and the characteristics of simple operation and flexible operation, which has certain practical value.
\end{英文摘要}

\begin{中文摘要}{密集预测；神经网络 ；特征对齐 ；安卓}
  密集预测是计算机视觉领域下的一类重要问题，这个问题对于自动驾驶，医学图像识别等领域的图像进行分割和理解具有重要价值；其包含了语义分割、实例分割、全景分割等多个子任务，近年来人们利用神经网络在这一问题上取得了突破。但在对于上卷积层利用插值法进行上采样的过程中，存在上采样得到的特征未与自下而上的卷积层的特征对齐的问题。对于这个问题，本文复现了FaPN（Feature-aligned Pyramid Network）中的特征对齐模块和特征选择模块，通过上采样前后的上下文信息对于上卷积层的关键特征进行选择和对齐。通过在COCO2017数据集上进行验证证实了模块对于小物体和物体边界预测的性能。并将其模块化，开发了一款简单的安卓APP。服务器端通过载入预训练模型提供服务，客户端提供了简单易用的UI界面和各类用户所需的相关功能。APP具有快速分割图像的功能和使用简单操作灵活的特点，具有一定的实用价值。
\end{中文摘要}


