% !Mode:: "TeX:UTF-8"
% !TEX program  = xelatex
\section{Conclusion and Future Work}
%In this paper, we illustrated the construction of our trajectory dataset from raw GPS data. Then we proposed the concept of trajectory-based road correlation and built a trajec- tory next-hop model to learn road embeddings and calculate road correlation matrix. Based on that, we gave the theory of refined adjacency matrix and integrated it into SOTA traf- fic prediction models to improve their performance. Extensive experiment results proved the effectiveness and robustness of our models. Following, a case study demonstrated the rationality of the road correlation.
%However, the road correlation matrix C is still a static representation of the road net- work graph. To strengthen its temporality, we are planning to extend our current work to study time-varying road correlations by splitting C into 24 hours and build a time-dynamic traffic prediction model.


%本文主要成果是复现了FaPN一文的实验结果并在COCO 2017和TT100K数据集上取得了分割结果。可以得出结论，FaPN中的FSM和FAM模块可以提升对于小物体和物体边界的预测性能，具有在原有模型基础上进一步提升效果的功能。本文将其实用化，包装为Android APP，将前后端进行解耦，实现了模型的通用化和模块化，提高了模型的实用性。

The main result of this paper is to reproduce the experimental results of the FaPN paper and obtain segmentation results on the COCO 2017 and TT100K datasets. It can be concluded that the FSM and FAM modules in FaPN can improve the prediction performance of small objects and object boundaries, with the function of further improving the effect based on the original model. This article puts it into practical use, packages it as an Android APP, decouples the front and back ends, realizes the generalization and modularization of the model, and improves the practicality of the model.

%其中对于服务器端模型的训练结果，在相同训练参数和环境的情况下达到了原模型FaPN的参考值，其相对于FPN网络有0.3\%到1.2\%不等的提升，特别是证明了在对于模型边界和小物体的预测上的提升。说明了选择模块和对齐模块的有效性。对于APP的最终结果，其应用了预训练的Mask RCNN和 Faster RCNN模型和移动端Paddle Lite模型，并在物体分割的问题上取得了较好的结果，在排除网络传输和模型加载的时间后，移动端Paddle Lite模型对于单张图片的分割结果平均在200ms，但因为其所调用的是移动端的AI推理引擎，限于计算力，分割结果与部署在服务端的模型仍存在差距。服务端的模型的平均分割时间在2s/Obj，但分割结果相对于移动端模型更精确，能识别的物体类型也更加丰富。

The training results of the server-side model have reached the reference value of the original model FaPN under the same training parameters and environment. Compared with the FPN network, it has an improvement ranging from 0.3\% to 1.2\%. Improved prediction of model boundaries and small objects. Illustrates the effectiveness of feature selection modules and feature alignment modules. For the final result of the APP, it applied the pre-trained Mask RCNN and Faster RCNN models and the mobile Paddle Lite model and achieved good results in the problem of object segmentation. After excluding the time of network transmission and model loading, The average segmentation result of the mobile Paddle Lite model for a single image is $200ms$, but because it calls the AI inference engine on the mobile side and is limited in computing power, there is still a gap between the segmentation results and the model deployed on the server-side. The average segmentation time of the server-side model is $2s/Obj$, but the segmentation results are more accurate than the mobile-side model, and the types of objects that can be recognized are also more abundant.

%但本文还存在诸多问题，比如模型可供选择的选项较少，训练的迭代次数较少导致无法完全复现原文的结果。由于服务器带宽问题，单张图像处理所需要的时间较长，并且无法实现实时分割的功能。APP的功能较为单一而且界面美观性较差等等。

However, there are many problems in this article, such that the model has fewer options to choose from, and the number of iterations of training is small, resulting in the inability to fully reproduce the results of the original text. Due to server bandwidth issues, single image processing takes a long time and the function of real-time segmentation is not possible. The function of the APP is relatively single, the interface is poorly aesthetically pleasing.